Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2020-08-02 article_springer/article_springer.Rmd
remove duplicate 'thanks', put grant support first

---
title: "Statistical Inference for inter-arrival times of extreme events in bursty time series"
# titlerunning: "CTRE: POT for Bursty Time Series"
thanks: |
    Peter Straka was supported by the 
    Discovery Early Career Research Award DE160101147 on the Project 
    "Predicting Extremes when Events Occur in Bursts" by the Australian
    Research Council.
    Katharina Hees was supported by 
    the DAAD co-financed by the German Federal Ministry of Education and 
    Research (BMBF).

@@

The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package. Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education and Research (BMBF).

>>>>

---
title: "Statistical Inference for inter-arrival times of extreme events in bursty time series"
# titlerunning: "CTRE: POT for Bursty Time Series"

@@

Peter Straka was supported by the Discovery 
Early Career Research Award DE160101147 on the Project 
“Predicting Extremes when Events Occurin Bursts” by 
the Australian Research Council. Katharina Hees was 
supported by the DAAD co-financed by the 
German Federal Ministry of Education and Research (BMBF).
The authors would like to thank Prof. Peter Scheffler for insights on 
stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
regarding the statistical methods and Gurtek Gill who helped create the 
MittagLeffleR R-package.
